A saturation model for impaired learning with enhanced plasticity: Supplementary material

### 2013-07-22 MHCpaper/MHCsupp.tex
typos in mhc supp

\newcommand{\captiontext}[1]{ can be found in \autoref{tr:#1} of \autoref{tab:params}.
  Time is measured in units of $1/r$, the mean time between plasticity events.
  (\ref{fig:#1_learn}) Learning curves for wild-type and \KO\ mutant with and without pre-training.
  (\ref{fig:#1_learnS}) Learning curves restricted to gain-increase training.
  (\ref{fig:#1_eq}) Equilibrium distributions without training or with gain-increase/decrease training for (\ref{fig:#1_eq_WT}) wild-type and (\ref{fig:#1_eq_KO}) \KO\ mutant,
  with states of weak synaptic strength to the left and strong states to the right.
  (\ref{fig:#1_pr}) Evolution of probability distributions for (\ref{fig:#1_pr_WT_nopre}\ref{fig:#1_pr_WT_pre}) wild-type and  (\ref{fig:#1_pr_KO_nopre}\ref{fig:#1_pr_KO_pre}) \KO\ mutant without (\ref{fig:#1_pr_WT_nopre},\ref{fig:#1_pr_KO_nopre}) and with (\ref{fig:#1_pr_WT_pre},\ref{fig:#1_pr_KO_pre}) pre-training,
  with states of weak synaptic strength at the top and strong states underneath. }

@@

\resultsfig{serial}{weak training}{($\Delta f=-0.1$)}{multistate_weak}

\resultsfig{serial}{moderate training}{($\Delta f=-0.3$)}{multistate_med}

\resultsfig{serial}{strong training}{($\Delta f=-0.45$)}{multistate_strong}

>>>>

\newcommand{\captiontext}[1]{ can be found in \autoref{tr:#1} of \autoref{tab:params}.
  Time is measured in units of $1/r$, the mean time between plasticity events.
  (\ref{fig:#1_learn}) Learning curves for wild-type and \KO\ mutant with and without pre-training.
  (\ref{fig:#1_learnS}) Learning curves restricted to gain-increase training.
  (\ref{fig:#1_eq}) Equilibrium distributions without training or with gain-increase/decrease training for (\ref{fig:#1_eq_WT}) wild-type and (\ref{fig:#1_eq_KO}) \KO\ mutant,
  with states of weak synaptic strength to the left and strong states to the right.
  (\ref{fig:#1_pr}) Evolution of probability distributions for (\ref{fig:#1_pr_WT_nopre},\ref{fig:#1_pr_WT_pre}) wild-type and  (\ref{fig:#1_pr_KO_nopre},\ref{fig:#1_pr_KO_pre}) \KO\ mutant without (\ref{fig:#1_pr_WT_nopre},\ref{fig:#1_pr_KO_nopre}) and with (\ref{fig:#1_pr_WT_pre},\ref{fig:#1_pr_KO_pre}) pre-training,
  with states of weak synaptic strength at the top and strong states underneath. }

@@

\resultsfig{serial}{weak training}{($\Delta f=0.1$)}{multistate_weak}

\resultsfig{serial}{moderate training}{($\Delta f=0.3$)}{multistate_med}

\resultsfig{serial}{strong training}{($\Delta f=0.45$)}{multistate_strong}
